---
title: 'Introduction to Linear Regression: Learnr Tutorial'
output: github_document
bibliography: "`r here::here('inst', 'packages.bib')`"
---

<!-- badges: start -->
<!-- badges: end -->

```{r knitr, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)
```

```{r setup, message = FALSE}
library(here)
```

```{r packages-bib}
knitr::write_bib(
  x = c("palmerpenguins", "tidyverse", "learnr", "gganimate"), 
  file = here::here("inst", "packages.bib")
)
```

## Purpose

This is a work-in-progress project to create an interactive tutorial on Linear
Regression, focussing (mostly) on concepts rather than code, and taking a highly
visual approach to showing how Linear Regression works.

```{r linear-regression-gif, out.width='55%', fig.align='center'}
gif <- "Rmd/linear-regression/images/linear-regression-anim-001.gif"
knitr::include_graphics(gif)
```

## Deployment

This learnr tutorial will be deployed on shinyapps.io when in a more complete
state. In the meantime, it can be run locally by cloning the git repository.

## Acknowledgements

This project depends heavily on the Palmer Penguins dataset [@R-palmerpenguins]
and the tidyverse suite [@R-tidyverse]. The tutorial is built with learnr 
[@R-learnr] and animated visuals are built with gganimate [@R-gganimate].

## License

The code is licensed under [MIT](https://github.com/tfzrch/learnr-linear-regression/blob/main/LICENSE).

Text, images, and other media are licensed, unless otherwise indicated, 
under [Creative Commons Attribution-NonCommercial 4.0 International (CC BY-NC 4.0)](https://creativecommons.org/licenses/by-nc/4.0/)

## References
