## Machine Learning

Think of machine learning as the art of building a 'thing labeller'.

The output of a machine learning project is a model. A model is just
a tool that when given inputs describing a 'thing' (attributes), gives back a 
'label' describing another attribute of that thing. These 'labels' can in fact 
be any type of data, such as continuous numeric values, not just textual or 
TRUE/FALSE categories.

In other words, a model is a 'recipe' for creating outputs from inputs, just 
like any function in any programming language.

$$
\color{#abe123}{Data} + \color{#abe123}{Recipe} \rightarrow \color{#1a99c1}{Label}
$$

### Make a Computer Write Your Recipe

Using a model is functionally the same as using a function. The real work for 
the data scientist in Machine Learning is building the model. Writing the 
recipe.

#### Traditional Programming

So what distinguishes Machine Learning from just writing a new function? Let's 
look at how we write a function:

```{r function_example, eval=FALSE, echo=TRUE}
add_two_sqrt <- function(x) {
  sqrt(x + 2)
}
```

What did I have to **know** about my output to write the recipe? Well, 
everything. 

I had to know that the output of this recipe will always be the square root of
the input plus 2. I had to know that the addition has to happen before the
square root. 

To make this function more efficient, I could even add in some checks to make 
sure the input is a number.

```{r function_example_checks, eval=FALSE, echo=TRUE}
add_two_sqrt <- function(x) {
  
  if (!is.numeric(x)) {
    stop("Supply a number")
  }
  
  sqrt(x + 2)
}
```

To write new functions, the programmer has to know everything there is about the
inputs it will receive and the output it will try to create from them, as the
recipe should always either fail to run (because of bad input) or follow the
recipe exactly to produce the same result for the same input.

#### Machine Learning

Machine Learning is for tasks where the recipe is not only unknown, but would be
really hard to discover and write out in code.

Instead of making the programmer do the hard work of discovering the recipe,
we'll let a computer do it instead.

We'll do this by giving the computer examples of input and outputs. If our
recipe is a cake, we'll give it lots of examples of cakes and the ingredients
needed to make them. The computer will then try to construct the recipe it needs
to make a good cake, and will evaluate how it did on every attempt by comparing
against the real cakes we gave it.

To use another analogy, think about how a child learns what is food and what is
not. Young children spend a lot of time putting things in their mouths, and they
learn to identify food from the feedback they get. Things that taste bad and 
can't be bitten are soon identified as 'not food'. Parents also provide feedback,
quickly rushing to stop the child from eating something dangerous or unclean.
Everything else, the child will learn to categories as 'food'.

```{r machine-learning-quiz}
quiz(
  question(
    "Which of these describes traditional progamming?",
    answer("The programmer supplies Data and the Recipe.", correct = T),
    answer("The programmer learns by examples"),
    answer("The computer supplies the Recipe")
  )
)
```